Transforming Trash as an Artistic Act

### 2015-12-06 chapter2_reduced.tex
Reduction
Former-commit-id: 5f9534d56a5913adc6ea4ef6840a4bdae4860f35

In this chapter trash and the practice of transforming trash is examined in theoretical and conceptual aspect. Theoretical foundations of trash are discussed. Further benefited from historical and social aspect of trash. It is questioned that how do scholars conceptualized the trash, what do they say about it?

Firstly we need to ask what is the source of trash. How is it generated? Secondly \ldots

%%%
%%%
%%%
\section{Throw away culture}
%%% Reference from Identity, mobility and the throwaway society
The term is actually a criticism of over consumption of short-live disposable objects.
\todo[inline]{We live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); (ref from another article)} whose behavioral pattern produce every time and everywhere. Even if conducted a qualitative research people are really do not throw away their things. \paraphrase{The research did not include the leftovers and detritus of food consumption packaging, bottles, and food waste, for example and neither was it concerned with another major category contributor to the volume of household waste, those `disposable' goods that are the primary means to maintaining bodily hygiene and cleanliness (Shove, 2003)}. They analyzed the things like television, furniture and toys like that.

\comment{Continuously consuming things and disposing of something. It is an important concept to understand why trash is trash? (or how it become trash?)}

(Our trash generating behavioral daily consumption patterns \ldots What are the results of them? Why are they throwing?) (There is a behavior that throws away and opposite of it there is a collecting behavior.)

\paraphrase{In this thesis the undeniable matter of waste, itself pressing, urgent and excessive, is used to infer the presence of a society defined by its generation; a society ceaselessly discarding and abandoning its surplus as excess, as part of an endless desire for the new. Morally corrupt and unequivocally environmentally damaging, the rhetoric of the throwaway society classifies discarding as intrinsically bad and commands us to assume control of our wasting, suggesting the adoption of heightened regulatory practices around disposal as the means to ensure that we clean-up our act. The thesis, however, lacks depth and provenance. It is, actually, glib. Indeed, to infer the presence of a throwaway society from contemporary levels of waste generation is problematic for at least four reasons.}

\comment{zaten zengin olanın atma lüksü var.}

\paraphrase{Life magazine fashionably heralded the advent of the "throwaway society" in 1955. 1971 daniel ingersoll reporting on his findings in the journal man in the notheast, "the industrial revolution ... was supplying the customer with hundreds of disposable containers and materials bt the end of the nineteenth century. the estimated 25.000 cubic yards of fill deposited in the upper portion of puddle dock show that the age of the throw away world began not in the twentieth century but during the nineteenth."} Therefore Industrial age played significant role (engine of the mountains of rubbish.)

% Resource is here: mmmacleo2005.pdf (throw away culture ile ilgili.) (Çünkü ben bunun ürününü kullanıyorum.)

\comment{All around of us filled with the things that are disposable. They are part of our daily activities.}

% not easily understandable with the entering non-art objects in art. artist are responding the current societies habits in a different ways. what they are doing here is to see other possibliteis and show actually what is going on. what does it mean all of these things.

\todo[inline]{Çevremiz tek kullanımlıklarla dolmuş taşmış durumda, bu iki sanatçıda bunları anlatıyor. Günlük alışkanlıkların, dikkaten kaçan şeylerin aslında farklı şeylere dönüşmesini görüyoruz. Bir anlamda çöplerin sanatçıların günlüklerine dönüştüklerini görüyoruz. Yani bir dönüşüm var. Benzer bir şey her gün yapılan işin fotoğrafını çeken insanda da var. Günlük rutinleri çöp üzerinden yakalayanlar var.}

\todo{need to elaborate}

@@

I began to save all of my coffee cups to use as "canvases" for making art. Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation and memories of a social moment upcycled from the detritus of our throw-away caffeine culture. I like my coffee or tea in a paper take-out cup. Even better than the contents, I like the used cup as a surface on which to draw and paint. And on the bottom of each one, I write the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment. Each cup representing a daily caffeine break. The installation makes visible largely unconscious patterns of consumption; this is what one simple take-away purchase looks like over the course of three years, this is what would usually be thrown away. It can be seen as a measure of time gone by, of money spent, of space to be taken up in a landfill. But as I upcycle each used cup into an artwork, it becomes the measure of other things as well: an artist's regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day. There are different versions of it. paintings on paper coffee cups displayed as installation in public window spaces. She publicly draw their cups (the cup art window installation and public drawing project were on view repeated showed at many places and date. During public drawing projects she draw with other people. and so. Buying a beverage is a daily event for Leech (and also many people. These coffee shops all around the world. As she drinks her coffee in the public, she also publicly transform its cup.

% TEA BAGS
% FROM https://instagram.com/silvirub/, http://www.rubysilvious.com/363-days-of-tea
\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/rubysilvious-teabag-Day169.jpg}
  \caption{Ruby Silvious, Day 169, 363 Days of Tea, 2015, Mixed media on upcycled paper tea bags, Dimensions variable}
  \label{fig:RubySilvious_TeaBag}
\end{figure}

Visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days. She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression. The project, entitled 363 Days of Tea, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations—the artist draws, paints, and forms collages on the salvaged tea bags. This project serves as Silvious’ daily journal, allowing her to record her thoughts and feelings by creating wonderful moody and whimsical designs on little teabag papers. Every day she creates a new piece that reflects her impressions in that moment. Currently based in New York, Silvious’ work has been exhibited internationally and she has received awards and recognition for her talents in paper work, print making and now her most recent endeavour of re-purposing recycled and found materials.

\begin{figure}[h!]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_OriginalView.jpg}
  \caption{Original view}
  \label{fig:ChrisJordan_Numbers_CloseView}
\end{subfigure}
\hfill
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_CloseView.jpg}
  \caption{Close view}
  \label{fig:ChrisJordan_Numbers_OriginalView}
\end{subfigure}
\caption{Caps Seurat, 2011 60x90" in one panel, and 88x132" in 3 panels}
\label{fig:ChrisJordan_Numbers_CapsSeurat}
\end{figure}

Depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute. Portraits of Global Mass culture from Chris Jordan. In Running the Numbers, photographer Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs. “There’s a disconnect that happens when we assume we know what we’re talking about when we talk about hundreds of millions of plastic bottles,” Jordan says. “I’m trying to translate these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension.” Many of Jordan's works are created from photographs of garbage and mass consumption Jordan uses everyday commonalities such as a plastic cup and defines the blind unawareness involved in American consumerism. His work, while often unsettling, is a bold message about unconscious behaviors in our everyday lives, leaving it to the viewer to draw conclusions about the inevitable consequences which will arise from our habits. He recreates the most remarkable artworks with combining bits of trashes as a mosaic. Here he draw attention to the our consumerism and express them numbers that are very big to understand. All the material that we have is trash to create this pictures.
\todo[inline]{Bu adam çok güzel bir şekilde küresel tüketimi ve onun sonuçlarını anlatıyor. Chris jordan hem bir gerçeği açığa çıkarıyor. Diğerinde ise belki de anlamamızı sor kılan gerçerkleri çöple ilgili, bizimle ilgili olanları gene bizim önümüze sunuyor. Bize konuya farklı bir açıdan bakmaya davet ediyor.}

%****************************************
% HAKAN GÜRSU
% Buraya aslında bir de Hakan Gürsu koymak gerekli olabilir. Yani aslında kendisi pek de sanatla ilgili bir laf etmiyor. Ama aslında tükettiğimiz onlarca şeye karşı bir tavır yaklaşım sergiliyor. Bu yüzden theory kısmında yer alabilir. Bu çöpün içinde boğulacağımızdan bahsediyor. Onu dönüştürmek gerekliliğinden yeteneğinden bahsediyor.

% TEZ STATEMENT.
% Ya gerçekten çöpü dönüştürüyorlar ya da çöpe dair düşünceleri dönüştürüyorlar, ve bunu ele alırken aslında heykel, kolaj, fotoğraf gibi şeylerden yararlanıyorlar ama aslında ortaya koydukları şey bir sanatsal eylem. veya bunu sanatsal eylem bağlamında ele alabiliriz.

% Aslında şöyle bir şey var mustafa, aslında sanatçının yaptığı şey ürünlerinden çok tekrar ve devamlı olarak eyleme geçirdiği yaklaşımı. Çöpün de bu tekrar eden yapısı buna uyum sağlıyor. Çünkü zaten hatayın sürekli bir parçası. Aslında bunun için şart olmasada destekleyici olduğu söylenebilir.

% Sanatçıların işlerine bir de bu açıdan baktığımızda ne görüyoruz.
%........................................

\comment{Things that are thrown away are one side of it. Actually all of our waste tells about us. ref required. Meaning of waste and what it tells about us. Understanding people through their wastes. REF. Tracey Emin's work. She opens up her wastes and also her life.}

% Related with tracy emin, photos of every cast off/discard/reject, understanding human through their discard.
\comment{GARBOLOGY} Garbology is a study of waste as a social science. Applying methodologies of archeology to the human debris. \todo[inline]{reference rubbish archeology of garbage} \paraphrase{"Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people. He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, “You are what you throw away.”" \cite{lukas2012garbage}}

% Garbology, from Encyclopedia, Abhijit Roy
\paraphrase{"The field of garbology involves the study of refuse and waste. It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture. According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s. A. J. Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970. It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973."}\todo{ref.}

% Rubbish: The Archeology of Garbage, p.24
\paraphrase{As noted, the Garbage Project has now been sorting and evaluating garbage, with scientific rigor, for two decades. The Project has proved durable because its findings have supplied a fresh perspective on what we know---and what we think we know---about certain aspects of our life. (example of Medical researches)} \todo{ref.}

@@

\paraphrase{Tracey Emin puts her private life to the public. The work, which Emin now describes as a portrait of a young woman. It is a time capsule. The cigarettes that litter the floor will one day no longer exist; neither will the newspapers. Around her there are pieces of junks speared all over the room. We can understand from her junk what type of life her has. We enter the world of artist through the her trashes.} \todo[inline]{Dört günden beri yataktan çıkmamış. İşte o sürede birikenler.}

%%%
%%%
%%%
% FROM Examined Life
\section{Zizek's Approach to Garbage}
(There is a curious fragment where Zizek, dressed as a sanitation man, stands in a waste deposit in a pile of garbage and ponders over garbage and human existence. In documentary film, Examined-life, Zizek talks about ecology in the middle of a garbage dump in London, and his part starts with these sentence: "This---garbage dump--- is where we should start feeling at home". He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology. Draw attention to notion of even if trash disappears from our world but not world. It seems as though the thrown out garbage disappears from our world. However, it disappears only from the world of illusions, but still exists in reality. He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing. He claims that it is ideological in the sense that wrong thinking important problems. Nature contains unimaginable catastrophes. think oil and distinct animals and plants. we profit balance part of the nature but it is created from catastrophe. Are we aware of this catastrophe. He asserts that ecology will slowly turn to religion that "is a kind of an unquestionable highest authority." Ideology of ecology warns us like, "Don't do that. It would be too much." its voice is like "Don't mess with D.N.A. Don't mess with nature. Don't do it" etc. We should not forget that we are part of the ecology. We must more alienated from the nature. We must find poetry and spirituality in the dimension of trash. That's the true love of world. Love is not about idealization. This part will be extended later.)

% FROM https://commons.wikimedia.org/wiki/File:Albatross_at_Midway_Atoll_Refuge_%288080507529%29.jpg
\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/ChrisJordan-Albatross.jpg}
  \caption{Chris Jordan, Albatross at Midway Atoll Refuge, 2009}
  \label{fig:ChrisJordan_Albatross}
\end{figure}

The unaltered stomach contents of a dead albatross chick photographed on Midway Atoll National Wildlife Refuge in the Pacific in September 2009 include plastic marine debris fed the chick by its parents.

Using spare narration and stunning imagery, Chris Jordan's feature film MIDWAY explores the plight of Laysan albatross plagued by the ingestion of our plastic trash. Both elegy and warning, the film explores the interconnectedness of species, with the albatross on Midway as a mirror of our humanity.

Even if garbage leave outs our life, we do not care about the results of it. And it is captured by the works of Chris Jordan.In this photo series it captures

% Effect of plastic on wildlife in Antartica.
% Her ne kadar biz çöpü attıktan bizim hayatımızdan çıksa da yok olmuyor. Sadece başka bir yerlere gidiyor. Mesela kuşların midelerine. Chris Jordan'ının imageları bunu çok da güzel açığa çıkartıyor. Bizim çöpleriminde habersiz hayvanlar bunları yiyorlar. Bir yandan ürettiğimiz ürünler ile kaynakları tüketirken bir diğer yandan ise artıklarımız diğer yaşanları tüketiyor. Dikkat çekmek istediğim nokta aslında ekolojik hassasiyetlerden çok aslında elimizde avucumuzda ne varsa onları tüketiyor olmamız. Karşı durduğum nokta ise tam olarak burası.

@@

His basic argument is that the modern eco movement is a conservative ideology. It says don't do X from an authoritarian high ground and it idolizes and mystifies ecology. Basically he says the eco movement has it's head in the clouds. If it loved the environment it would recognize the rubbish we create and the chaotic nature of ecological change and try to further divorce itself from that process(nature) and try to turn the whole thing into art.

\begin{itemize}
\item Our relation to our filth follows an “out of sight, out of mind” principle, but trash doesn’t disappear.
\item Ideology addresses real problems but mystifies them.
\item We search for meaning when a horrible event happens to make it easier to accept.
\item The ideology of ecology is that world is in the best possible state and that humans disturb nature.
\item Nature is not an organism in balance that humans exploit, but rather a series of great catastrophes.
\item Ecology is becoming more like religion with dogmas.
\item Even if we learn the potential catastrophes of nature, we ignore them as long as they don’t manifest near us.
\item The solution is not to worry about saving nature, but to figure out how to survive without it by becoming more artificial.
\item Learn to love our trash as a part of ecology.
\end{itemize}

How much harmonious all these produced materials with nature? How many animals and the plant can use these discarded items? (Because of complex production methods their recycling requires complex processes again. Some of them already produced to protect goods from natural factors (like decaying etc.). However how can we protect nature from them?) It is very hard that spontaneously they become harmonious with nature. However, some artists turned to trash into site-specific sculptures that are more than trash heap. not discarding but bracing our attitudes turned them to a something that worth it to watch and think about it. (Converting what we create harmonious with the existing system.) Because it is not possible to think that nature will live harmoniously what we created. The more likely idea will be we will live harmoniously with what we create.

Getting rid of it is not the significant action. It still waits us at somewhere else or the next generations have to cope with it. (Establish relationship with the afterthought.) Maybe the first thing to do is accept the trash, to accept that there are things out there that serve nothing. To break out of this eternal cycle of functioning.

The issue of trash is not limited with ecological and economic perspective, it has also other dimensions.(draw attention to multidimensionality of this topic, but why? and what are the other dimensions?)

Trash itself is not the only problem, the practice, lifestyle causing it is more important problem. The dynamics of market and flow of objects into it plays important role production of trash.

Trash of developed societies has higher decomposing period in the nature. Therefore results in higher damage to the nature, hard to reuse, hard to transform, sometimes not to safe to keep them because toxic elements etc.

\textbf{Summary.} Zizek mentions that ecology is something wrong point to approach this topic. Show the problematic understanding thought to the garbage. Suggest another thing, and point out the need for the new approach. Beyond the ecological problem there are different sides of it. Different readings can be added to the topic. Adding spirituality and new aesthetics dimension to the topic.

>>>>

%
%
In this chapter trash and the practice of transforming trash is examined in theoretical and conceptual aspect. Theoretical foundations of trash (Rubbish Theory) are discussed. Beyond common perception and dictionary meaning of trash alternative or different approaches are examined with help of ideas of philosophers (Zizek). Focused on the type of trash (disposable, single-use trash) and questioned the behavioural pattern that generates mountains of trash with these disposable trash. Further it is mentioned how artist are approached these notions? and how their work viewed as their offered window or framework.

%
%
\section{Throw away culture}
[What is questioned in this section?] Firstly we need to ask what is the source of trash. How is it generated? Secondly what are the behaviors behind the producing trash?

%
%
[Disposable items.] \comment{Disposable: made to be used once or only a few times. Made to be thrown away after one use or several uses. Not permanent or durable. Not designed to reuse again and again. For examples packages of bevarages, paper cups etc. They are used very short-time. Their lifetime can be measured in minutes in terms of usage. I have never seen such person that uses own paper cup again and again. However their usage durations are very short, they continue to exist in the nature.} \todo{transition gerekli.} \paraphrase{The strange think about many products that are produced these days is that they are not made to last for a long time. Importantly the term throw away society has a slightly negative connotation, or meaning. When you describe a society as a throw away society, you are probably critising that behaviours or showing your disapproval. \todo{ref.}}

\paraphrase{being wasteful in the ways we live is encouraged, expected and in many instances impossible to avoid (Hawkins 2006: x)}

Disposable items are first introduced X and their usage accelerated after Y. There are Z factors that give rise to usage of single-use ites excessively \todo{Bu cümleyi doğru düzgün kurmak gerekli.}.

% Reference from Identity, mobility and the throwaway society
[The term throwaway culture] Life magazine first introduced the term "throw-away" mentioning that behavioral pattern of society \todo{life magazine tekrar bak.}. \comment{Scholars argue that contemporary societies are throwaway societies (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003) \todo{ref required.}.} The term is actually a criticism of over consumption of short-live disposable objects. \comment{The term overconsumption refers to a way of living in which the lifestyle patterns of human beings lead to an accelerated expenditure of natural resources.}

\paraphrase{Life magazine fashionably heralded the advent of the "throwaway society" in 1955. 1971 daniel ingersoll reporting on his findings in the journal man in the notheast, "the industrial revolution ... was supplying the customer with hundreds of disposable containers and materials bt the end of the nineteenth century. the estimated 25.000 cubic yards of fill deposited in the upper portion of puddle dock show that the age of the throw away world began not in the twentieth century but during the nineteenth."} \todo{ref. Hangi kaynaktan?}

% Reference from Identity, mobility and the throwaway society
[Counter-argument] Even if conducted a qualitative research people are really do not throw away their things. \paraphrase{The research did not include the leftovers and detritus of food consumption packaging, bottles, and food waste, for example and neither was it concerned with another major category contributor to the volume of household waste, those `disposable' goods that are the primary means to maintaining bodily hygiene and cleanliness (Shove, 2003)}. They analyzed the things like television, furniture and toys like that.

[Factors.] \comment{Not only one factor, technological advacements can be one of them. These items with the help of industrialization can be produced easily. Mass production. Disposable items are reduces the labour and human resources as compared to the traditional ways (Consider napkin vs wipes, glass vs paper cup). Another point is that they are more affordable in terms of supply chain and cost. In other words you can put new one easily. Therefore there is no need to save the old one. Last but not least increasing attention of hygine is contributed to the extension of disposables in the market highly.} \paraphrase{The commodities of food and drink must be safe, sterile and private.} \todo{ref. ontology of trash}

\paraphrase{Taken to its obsessive extreme, the germ theory proscribes companionship. The Latin root for this word, cum pani, literally means to share bread. But insofar as each eater harbors untold numbers of hazardous germs, it is safest to keep one’s food strictly to one’s self. Safety in a world of bacteria implies isolation. Packaging successfully isolates both food and consumer within a structure of sterile control. In essence, it encloses the commons. Susan Strasser narrates part of the history of this enclosure through the career of the disposable drinking cup, which appeared in the early years of the twentieth century. \todo{ref. ontology of trash}}

\begin{quote}
While the sanitary advantages of toilet paper might have been obvious, those of the paper cup required a belief in germs. The widespread use of paper cups was a direct result of a public health crusade educating people about the invisible organisms spread by the common drinking cups once standard in public places, especially trains and railroad stations. Manufacturers of paper cups teamed up with public health authorities to campaign for federal and state regulations banning common drinking cups from use in interstate traffic. Succeeding in 1912, they competed for the business of the railroads and train stations\ldots
Disposable paper cups met significant resistance. Most public places offered them in coin-operated dispensers, and some people were not willing to pay for what had once been free. Respectable travellers carried their own cups, available in metal and celluloid in a variety of collapsable and folding designs. Others reused paper cups from the trash or drank out of the public tanks, putting their lips to the faucet or using the cover of the tank as a cup. Some people protested against the vending machines: soldiers smashed paper cup dispensers in Washington’s Union Station during President Wilson’s inauguration in 1913. And some public places installed drinking fountains instead of paper cups dispensers, although at first these, too, were attacked as unsanitary because people could touch the nozzle with their lips.
\end{quote}

[Dark side.] Usage of disposable items in the society is very widespread. For same cases it is inevitable. Beyond the advantages of disposable items there are side of effects of consuming them excessively. They result in mountains of garbage.

\comment{Handling of this mountains of garbage is another topic. It is not the topic of this thesis. It is not debated that usage of disposals are supported or not supported. It might be subject of another thesis. What is important here the results of it and the reflection of the artist.} \comment{Buna karşı geliştirilen bir refleks olduğu için bu kısma giriyorum. Aynı zamanda ben de bu ürünü kullanıyorum. Konuyu o yüzden farkl açılarından anlamak gerekli. \todo{Ama benim konuya nasıl yaklaştığım biraz belirsiz.}}

[Art] There are some artists whose works are related with the pheomena expressed above. (Some of the works of artist can be examined in this pheomena.)

% ARTWORK
% Portraits of Global Mass culture
\begin{figure}[h!]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_OriginalView.jpg}
  \caption{Original view}
  \label{fig:ChrisJordan_Numbers_CloseView}
\end{subfigure}
\hfill
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_CloseView.jpg}
  \caption{Close view}
  \label{fig:ChrisJordan_Numbers_OriginalView}
\end{subfigure}
\caption{Caps Seurat, 2011 60x90" in one panel, and 88x132" in 3 panels}
\label{fig:ChrisJordan_Numbers_CapsSeurat}
\end{figure}

Chris Jordan creates digital photographic series that turns numbers to visuals. Provide different way to understand the statistics and the missed reality of consumerism. Creates gigantic prints to express numbers in a visual manner. Draws attention the the global consumerism. reveals the reality that is hard to understand. Because it is spread to the community and time.

\paraphrase{Portraits of Global Mass culture from Chris Jordan. Depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute. In Running the Numbers, photographer Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs. “There’s a disconnect that happens when we assume we know what we’re talking about when we talk about hundreds of millions of plastic bottles,” Jordan says. “I’m trying to translate these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension.” Many of Jordan's works are created from photographs of garbage and mass consumption Jordan uses everyday commonalities such as a plastic cup and defines the blind unawareness involved in American consumerism. His work, while often unsettling, is a bold message about unconscious behaviors in our everyday lives, leaving it to the viewer to draw conclusions about the inevitable consequences which will arise from our habits. He recreates the most remarkable artworks with combining bits of trashes as a mosaic. Here he draw attention to the our consumerism and express them numbers that are very big to understand. All the material that we have is trash to create this pictures.}

[CRITICS] Visuals of Chris jordan are like modern versions of mosaics. In the age of consumption the most easily accessible matariel is trash. Trash has different colors and sizes and shapes. Therefore it is a perfect material to build sculptures from them. There is a great diversity of trashes and offers new alternatives.

Not every people throw away disposible objects, some of them save them and use for their own purposes.

% ARTWORK
% TEA BAGS
% FROM https://instagram.com/silvirub/, http://www.rubysilvious.com/363-days-of-tea
\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/rubysilvious-teabag-Day169.jpg}
  \caption{Ruby Silvious, Day 169, 363 Days of Tea, 2015, Mixed media on upcycled paper tea bags, Dimensions variable}
  \label{fig:RubySilvious_TeaBag}
\end{figure}

\paraphrase{Visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days. She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression. The project, entitled 363 Days of Tea, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations—the artist draws, paints, and forms collages on the salvaged tea bags. This project serves as Silvious’ daily journal, allowing her to record her thoughts and feelings by creating wonderful moody and whimsical designs on little teabag papers. Every day she creates a new piece that reflects her impressions in that moment. endeavour of re-purposing recycled and found materials.} \todo{cite website}

[CRITICS] This work is for fathers day. Works of Silvious catch the important moments of days and can be as a diary (or a record of that moment and day). Trashes trasnformed to diaries. Trash is every where, already at hand.

@@

\paraphrase{I began to save all of my coffee cups to use as "canvases" for making art. Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation and memories of a social moment upcycled from the detritus of our throw-away caffeine culture. I like my coffee or tea in a paper take-out cup. Even better than the contents, I like the used cup as a surface on which to draw and paint. And on the bottom of each one, I write the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment. Each cup representing a daily caffeine break. The installation makes visible largely unconscious patterns of consumption; this is what one simple take-away purchase looks like over the course of three years, this is what would usually be thrown away. It can be seen as a measure of time gone by, of money spent, of space to be taken up in a landfill. But as I upcycle each used cup into an artwork, it becomes the measure of other things as well: an artist's regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day. There are different versions of it. paintings on paper coffee cups displayed as installation in public window spaces. She publicly draw their cups (the cup art window installation and public drawing project were on view repeated showed at many places and date. During public drawing projects she draw with other people. and so. Buying a beverage is a daily event for Leech (and also many people. These coffee shops all around the world. As she drinks her coffee in the public, she also publicly transform its cup.} \todo{cite her website}

[CRITICS] inside of glass window. public space. publicly drawing, as she drinks her coffee publicly, also paints them publicly.

%
%
\todo{transition needed.} [TRASH and POTRAIT OF PEOPLE] Trash tells about societies and also reveals personal aspects of peoples life. What people consume is actually tells many things about them \todo{Bununla ilgili bir sürü referans var, onları buraya ekle.}. As scholars mentioned that throughout the discards of someone else many thing can be understand. They are end product of our activities and it can be traced through the discard and garbage.

%
%
[GARBOLOGY] Garbology is a study of waste as a social science. Applying methodologies of archeology to the human debris.

\paraphrase{Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people. He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, \quotes{You are what you throw away.}" \cite{lukas2012garbage}}

% Garbology, from Encyclopedia, Abhijit Roy
\paraphrase{The field of garbology involves the study of refuse and waste. It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture. According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s. Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970. It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973.}\todo{ref.}

\paraphrase{the work of archaeologists such as William Rathje and Cullen Murphy has offered significant insights into the relationship between archaeological artefacts and garbage, exploring the function of trash as a resource for understanding cultural and social practice. At the same time, thinkers such as Zygmunt Bauman and Giorgio Agamben have shed light on the fate of   the human being as a wasted or discarded element in discourses of socio-political hygiene. (from Trash Culture)}

\todo{transition needed.} With the help above understanding of trash, what can we see the work of arts. For examples tracey emin.

@@

\paraphrase{Tracey Emin puts her private life to the public. The work, which Emin now describes as a portrait of a young woman. It is a time capsule. The cigarettes that litter the floor will one day no longer exist; neither will the newspapers. Around her there are pieces of junks speared all over the room. We can understand from her junk what type of life her has. We enter the world of artist through the her trashes.} \todo{Hastalık dönemi... Sanattaki yerine bakmak gerekli.}

%
%
\section{Zizek's Approach to Rubbish}
[Transition, introduction] 
\todo{Adam bir transition bulmalı buraya.} Last decades increasing attention the the ecology and rubbish. This section is related with the increasing interest on ecology. Global warming is one of them, plastic pollution on the oceans also is part of it. These types of news and talks increasingly find a place on media more and more. Zizek comments on ecology and trash.

In documentary film, Examined-life, Zizek, dressed as a sanitation man, talks about ecology in the middle of a garbage dump in London. His part starts with these sentence: \quote{This [garbage dump] is where we should start feeling at home}.

Draws attention to notion of even if trash disappears from our world but not world. It seems as though the thrown out garbage disappears from our world. However, it disappears only from the world of illusions, but still exists in reality. \comment{Getting rid of it is not action of production. It is action of ignorance. It still waits us at somewhere else or the next generations will have to cope with it. Maybe (as Zizek suggest) the first thing to do is accept the trash.}

He asserts his claim at first and go through explaining how ecology turns to ideology and mentions wrong perception about the ecology. He thinks that the way of approaching ecology is problematic, because accepting that nature as a balanced harmonious thing. He claims that it is ideological in the sense that wrong thinking important problems. Nature contains unimaginable catastrophes. Consider distinction of animals and creation of oil. People profit from the balance of the nature but it is created from a series of catastrophes. He asserts that ecology will slowly turn to religion that \quotes{is a kind of an unquestionable highest authority.} Ideology of ecology warns us like, \quotes{Don't do that. It would be too much.} its voice is like \quotes{Don't mess with D.N.A. Don't mess with nature. Don't do it} etc. He suggests that people must more alienated from the nature. They must find poetry and spirituality in the dimension of trash. That's the true love of world. Love is not about idealization. Therefore he thinks that garbage dump is a place that people should accept it as a home.

@@

\paraphrase{His basic argument is that the modern eco movement is a conservative ideology. It says don't do X from an authoritarian high ground and it idolizes and mystifies ecology. Basically he says the eco movement has it's head in the clouds. If it loved the environment it would recognize the rubbish we create and the chaotic nature of ecological change and try to further divorce itself from that process(nature) and try to turn the whole thing into art.}

Some of his ideas can be summarized as follows:
\begin{itemize}
\item Our relation to our filth follows an “out of sight, out of mind” principle, but trash doesn’t disappear.
\item Ideology addresses real problems but mystifies them.
\item We search for meaning when a horrible event happens to make it easier to accept.
\item The ideology of ecology is that world is in the best possible state and that humans disturb nature.
\item Nature is not an organism in balance that humans exploit, but rather a series of great catastrophes.
\item Ecology is becoming more like religion with dogmas.
\item Even if we learn the potential catastrophes of nature, we ignore them as long as they don’t manifest near us.
\item The solution is not to worry about saving nature, but to figure out how to survive without it by becoming more artificial.
\item Learn to love our trash as a part of ecology.
\end{itemize}

Some artists turned to trash into site-specific sculptures that are more than trash heap after their intervantion. Not discarding but bracing our attitudes turned them to a something that worth it to watch and think about it. (Converting what we create harmonious with the existing system. Because it is not possible to think that nature will live harmoniously what we created. The more likely idea will be we will live harmoniously with what we create.) Turning trash to things that can be lived together \todo{Buraya sanat işi gelebilir, özellikle kamusal alana yapılan çöten heykel işleri gibi.}.

\todo{needs a discussion.}

[Summary.] \comment{Sürekli çöpü kendimizden uzak tutmaya çalışırken aslında zizek bize bunun tam da tersini yapmamızı bize öneriyor. Bu adam aslında insanlar doğaya zarar vermiyorlar demiyor. Onun dediği aslında yanlış sebep sonuç ilişkileri kurduğumuz üzerinden gidiyor. Çöpü tekrar ele aldığımızda ise yep yeni şeyler keşfedeğiz. Yeni alternatifler oluşacak. Aslında yeni bir dünya kurgulanacak. Çöp nasıl dönüştürülecekse, çöp de insanları dönüştürecek.}

Transforming trash is not related with ecological perspective. We are not trying to save the planet earth or mother nature. Beyond ecological concerns we are trying to find ways to live our trash.

Zizek mentions that ecology is something wrong point to approach trash. Shows the problematic understanding of garbage. Suggest another thing, and point out the need for the new approach. Beyond the ecological problem there are different sides of it. Different readings can be added to the topic. Adding spirituality and new aesthetics dimension to the topic.

Idealization of nature is problematic. Loving nature is loving trash. Live with trash. Do not see it as trash actually. Then the question is How to love trash? How to live with trash? Think beyond the common perception. Do not think it as abject, disgust. Can living with our trash enrich (our perceptions, abilities)? How not to see them as trash and useless? Can it be possible with art?

\todo{Çöp evler buraya gelebilir belki, çöpleriyle birlikte yaşayanlar?}

%
%
\section{Rubbish Theory}

\comment{Çöpün hep çöp gibi kalmadığı ve farklı bakış açıları olabileceğini gördük. Bu hareketlilik ve farklılık ise bir teorik çerçeveye oturulmuş, hadi ona baklım şimdi. Zaten bu hayatta çöp her zaman karşımıza çöp olarak çıkmıyor.}

In this thesis transformation of trash is claimed and this theory provides a framework for this transformation.

\paraphrase{Michael Thompson’s 1979 study Rubbish Theory elaborated an understanding of rubbish as part of a flexible and shifting system of value construction, underlying notions of innovation, creativity and social status \todo{ref. from Trash Culture}.}
